---
title: "p8105_hw1_tz2659"
author: "Tracy Zhu"
date: "2024-09-21"
output: html_document
---
## Problem 1
```{r}
data("penguins", package = "palmerpenguins")
```

The `penguins` dataset contains `r nrow(penguins)` rows and `r ncol(penguins)` columns. This dataset measures 3 species of penguins (`r paste(unique(penguins$species), collapse = ", ")`) on 3 places: `r paste(unique(penguins$island), collapse = ", ")`.

The important variables includes: 
1. Species: The three species are `r paste(unique(penguins$species), collapse = ", ")`.
2. Island: Penguins were observed on `r paste(unique(penguins$island), collapse = ", ")`.
3. Bill Length (bill_length_mm): This variable ranges from `r range(penguins$bill_length_mm, na.rm = TRUE)[1]` mm to `r range(penguins$bill_length_mm, na.rm = TRUE)[2]` mm.
4. Bill Depth (bill_depth_mm): This variable ranges from `r range(penguins$bill_depth_mm, na.rm = TRUE)[1]` mm to `r range(penguins$bill_depth_mm, na.rm = TRUE)[2]` mm.
5. Flipper Length (flipper_length_mm): The length ranges from `r range(penguins$flipper_length_mm, na.rm = TRUE)[1]` mm to `r range(penguins$flipper_length_mm, na.rm = TRUE)[2]` mm. The mean is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.
6. Body Mass (body_mass_g): This variable ranges from `r range(penguins$body_mass_g, na.rm = TRUE)[1]` g to `r range(penguins$body_mass_g, na.rm = TRUE)[2]` g.
7. Year (year): Year is from `r range(penguins$year, na.rm = TRUE)[1]` to `r range(penguins$year, na.rm = TRUE)[2]`
8. The dataset also includes the `sex` of the penguins which are female and male.

```{r}
library(ggplot2)

scatterplot <- ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(x = "Bill Length (mm)",
       y = "Flipper Length (mm)",
       color = "Species") +  
  theme_minimal()
print(scatterplot)

ggsave(filename = "scatterplot_flipper_vs_bill.png", plot = scatterplot)

```

