---
title: "p8105_hw1_tz2659"
author: "Tracy Zhu"
date: "2024-09-21"
output: html_document
---
## Problem 1
```{r}
data("penguins", package = "palmerpenguins")
```

The `penguins` dataset contains `r nrow(penguins)` rows and `r ncol(penguins)` columns. This dataset measures 3 species of penguins (`r paste(unique(penguins$species), collapse = ", ")`) on 3 places: `r paste(unique(penguins$island), collapse = ", ")`.

The important variables includes: 
1. Species: The three species are `r paste(unique(penguins$species), collapse = ", ")`.
2. Island: Penguins were observed on `r paste(unique(penguins$island), collapse = ", ")`.
3. Bill Length (bill_length_mm): This variable ranges from `r range(penguins$bill_length_mm, na.rm = TRUE)[1]` mm to `r range(penguins$bill_length_mm, na.rm = TRUE)[2]` mm.
4. Bill Depth (bill_depth_mm): This variable ranges from `r range(penguins$bill_depth_mm, na.rm = TRUE)[1]` mm to `r range(penguins$bill_depth_mm, na.rm = TRUE)[2]` mm.
5. Flipper Length (flipper_length_mm): The length ranges from `r range(penguins$flipper_length_mm, na.rm = TRUE)[1]` mm to `r range(penguins$flipper_length_mm, na.rm = TRUE)[2]` mm. The mean is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.
6. Body Mass (body_mass_g): This variable ranges from `r range(penguins$body_mass_g, na.rm = TRUE)[1]` g to `r range(penguins$body_mass_g, na.rm = TRUE)[2]` g.
7. Year (year): Year is from `r range(penguins$year, na.rm = TRUE)[1]` to `r range(penguins$year, na.rm = TRUE)[2]`
8. The dataset also includes the `sex` of the penguins which are female and male.

```{r}
library(ggplot2)

scatterplot <- ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(x = "Bill Length (mm)",
       y = "Flipper Length (mm)",
       color = "Species") +  
  theme_minimal()
print(scatterplot)

ggsave(filename = "scatterplot_flipper_vs_bill.png", plot = scatterplot)
```

## Problem 2
### Create a data frame:
```{r}
library(tidyverse)
set.seed(2024)

df <- data.frame(
  random_sample = rnorm(10),                         
  logical_vector = rnorm(10) > 0,                       
  character_vector = letters[1:10],                    
  factor_vector = factor(rep(c("Level1", "Level2", "Level3"), length.out = 10))  
)
print(df)
```

### Take the mean of each variable
```{r}
mean_random_sample <- mean(pull(df, random_sample)) # Works because it's numeric
mean_logical_vector <- mean(pull(df, logical_vector)) # Works because TRUE = 1, FALSE = 0
mean_character_vector <- mean(pull(df, character_vector)) # Error because it's a character 
mean_factor_vector <- mean(pull(df, factor_vector)) # Error because it's a factor
```

### Convert variables from one type to another
```{r}
numeric_logical <- as.numeric(df$logical_vector) # TRUE = 1, FALSE = 0
numeric_character <- as.numeric(df$character_vector) # Converts to NA because characters cannot become to numeric
numeric_factor <- as.numeric(df$factor_vector) # Converts to the next level
```

